\ttitle

### 2014-01-09 Chapters/Chapter4/data_gathering.tex
Add boxplot and remarks real-world results
Finalizing.... still....and again...

For the experiments we used a HTC Sensation XE smartphone as recording device.
The activities were recorded using a free Android application \cite{sensorlogger}.
This application was chosen for its convenient data format of the sensor recording and its regularity of the sampling interval.
Table~\ref{tab:recorded_metrics} lists all the recorded metrics.
For our expiments we used the data for the accelerometer, magnatief field and rotation.

>>>>

For the experiments we used a smartphone with inertial sensors as recording device.
The activities were recorded using a free \textsc{Android} application \cite{sensorlogger}.
This application was chosen for its convenient data format of the sensor recording and its regularity of the sampling interval.
Table~\ref{tab:recorded_metrics} lists all the recorded metrics.
For our expiments we used the data for the accelerometer, magnatief field and rotation.

We implemented our algorithm in \textsc{MATLAB}.
For the \gls{svdd} model construction phase we used the \textsc{dd\_tools} library by Tax \cite{Ddtools2013}, which is dependend on the \textsc{PR\_tools} package, originating from \cite{van2005classification}.
In an earlier attempt we used the a \textsc{LibSVM} \cite{chang2011libsvm} add-on for the \gls{svdd} algorithm \cite{changrevisit}, but we had troubles making that implementation work with our data.

### 2014-01-09 Chapters/Chapter6.tex
Finalizing.... still....and again...

In this chapter we discuss the real-world data sets used for this research and the performance of our proposed algorithm on these data sets.
In \Cref{sec:data_sets} we discuss common available data sets and argue that these are inappropriate for our research.
It is followed by an overview of the setup we have created to record our own continuous data sets in an uncontrolled environment, both for in- and outdoor activities.
The series of activities performed are discussed in \Cref{sec:data_gathering}.
In that section we show typical plots of the inertial sensor data and stills from the video recordings.
That will illustrate the setting in which the activities are performed and the characteristics of continuous data.
Finally, the results of the algorithm are discussed in \Cref{sec:real_world_results}.
We will use the objective measures, introduced in \Cref{sec:artificial_data_quality_metrics}, and also try to give subjective claims on the performance of the algorithm applied to the real-world data.

>>>>

In this chapter we discuss the real-world data sets used for this research and the performance of our proposed algorithm on these data sets.
In \Cref{sec:data_sets} we discuss common available data sets and argue that these are inappropriate for our research.
It is followed by an overview of the setup we have created to record our own continuous data sets in an uncontrolled environment, both for in- and outdoor activities.
The series of activities performed are discussed in \Cref{sec:data_gathering}.
In that section we show typical plots of the inertial sensor data and stills from the video recordings.
That will illustrate the setting in which the activities are performed and the characteristics of continuous data.
Finally, the results of the algorithm are discussed in \Cref{sec:real_world_results}.
We will use the objective measures, introduced in \Cref{sec:artificial_data_quality_metrics}, and also give subjective claims on the performance of the algorithm applied to the real-world data.
Since the data sets used are real-world recordings, we will put emphasis on the latter type of quality measures \ie the subjective claims.

### 2014-01-09 Chapters/Chapter6/data_gathering.tex
Finalizing.... still....and again...

% !TEX root = ../../main.tex
\section{Data Gathering}\label{sec:data_gathering}
\TODO{Determine subjects:}
\begin{enumerate}
  \item Roemer?
  \item Jos?
  \item Marc
\end{enumerate}
For our data sets of real world activities we have sampled both in- and outdoor activities.
The subjects performing the activities are three males, of an age around 25.
We have used two series of recordings.
The first series consists of various outdoor recordings with segments of walking, running and standing.
Some activities are performed in a straight line, whilst others are performed around corners or in a wide circular direction.
The second series consists mainly of walking up and down the stairs, with small vertical parts between the segments.
The stairs are all in a circular shape.

\subsection{Outdoor straight lines}\label{subsec:outdoor_straight}
The first series of outdoor performed activities consist of walking and running segments in a straight line.
Halfway the recording is a $180^{\circ}$ turn.
The activities consist of standing still, walking and running (both jogging and sprinting).
The plots of \Cref{fig:plots_subject_1} shows the recordings of Subject $1$.
For Subject $2$ the plots are visible in \Cref{fig:plots_subject_2}.
The recorded metrics originate from the accelerometer, rotational and magnetometer sensors.
The solid black lines indicate manually annoted change points, the dashes lines indicate the closest discovered change point.
A still from the video recording, showing Subject $2$ performing a (sprinting) run segment, is in \Cref{fig:stills_subject_2_sprinting}.

% \begin{center}\begin{table}
%   \begin{tabulary}{\textwidth}{|l|c|c|}
%     \hline
%     \multicolumn{3}{|c|}{Subj 1, run 1} \\
%     \hline \hline
%     Act. & Ann. & Disc. \\
%     \hline
%     Still & 0 & *0* \\
%     \hline
%     Shake & 3.5 & *3.5* \\
%     \hline
%     Still & 4.2 & *4.2* \\
%     \hline
%     In pocket & 5.5 & *5.5* \\
%     \hline
%     Walk & 7 & *7* \\
%     \hline
%     Run & 10 & *10* \\
%     \hline
%     Walk & 14 & *14* \\
%     \hline
%     Run & 17.2 & *17.2* \\
%     \hline
%     Walk & 22.1 & *22.1* \\
%     \hline
%     Turn CCW & 23.5 & *23.5* \\
%     \hline
%     Walk & 24.2 & *24.2* \\
%     \hline
%     Run (sprint) & 28 & *28* \\
%     \hline
%     Run & 31 & *31* \\
%     \hline
%     Walk & 33 & *33* \\
%     \hline
%     Run & 35.5 & *35.5* \\
%     \hline
%     Walk & 39 & *39* \\
%     \hline
%     Out pocket & 41 & *41* \\
%     \hline
%     Still & 43 & *43* \\
%     \hline
%     \hline
%     \multicolumn{2}{|l|}{Ratio Total CPs} & 3.2 \\
%     \hline
%     \multicolumn{2}{|l|}{Sum of differences} & 12.341 \\
%     \hline
%   \end{tabulary}
%   \caption[Performed activities subject 1 run 1]{The outdoor series performed activities by subject 1, run 1.}
%   \label{tab:outdoor_series}
% \end{table}\end{center}

% ===== OUTDOOR FREE ACTIVITIES ========
\subsection{Outdoor free}\label{subsec:outdoor_free}
The second series of outdoor recordings consist of more free-form activities.
The performed activities consist, as with the first set, of standing, walking, and running.
Furthermore, the segments are performed in a circular manner.
\eg the running activities are performed around a fountain with an estimated diameter of 10 meters.
The plots of the recordings of Subject, for the accelerometer, rotation, and magnetometer are shown in...
\TODO{Add plots}
For Subject~$2$ the still of the video recordings are in the upper row of \Cref{fig:stills_subject_1_and_2}, for Subject~$1$ in the lower row.

@@

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
    \caption{Magnetic Field}
    \label{fig:recording_subject_1_run_1_magnetic}
  \end{subfigure} \\
  \caption[Plots]{Annotated plots of a full recording performed by Subject~$2$. The vertical lines are manually determined change points. The label above each segment indicates the current performed activity.}\label{fig:plots_subject_1}
\end{figure}

@@

\subsection{Indoor stairs}\label{subsec:indoor_stairs}
The final series of activities recorded consist of walking up and down the stairs, indoor.
The stairs are shaped in an semi-circular form, with a small vertical segment on each floor.
The still of \Cref{fig:stills_subject_3_downstairs} illustrates the circular shape of the stairs.
In \Cref{fig:stills_subject_3_upstairs} the small flat segment is visible.
Between the stairs the subject walked in a hallway with a $180^{\circ}$ counter-clockwise turn, as shown in \Cref{fig:stills_subject_3_walking}.
The recorded sensor data of the performed activities are visible in the plots of \Cref{fig:data_gathering_run_3_rot,fig:data_gathering_run_3_mag,fig:data_gathering_run_3_acc}.

>>>>

% !TEX root = ../../main.tex
\section{Data Gathering}\label{sec:data_gathering}
For our data sets of real-world activities we have sampled both in- and outdoor activities.
The subjects performing the activities are three males, of an age around 25.
We have used four types of recordings.
The first type (Run 1 and Run 2) consists of various outdoor recordings with segments of walking, running and standing.
For the second type (Run 4, 5, and 6) some of the same activities are performed in a straight line, whilst others are performed around corners or in a wide circular direction.
The third type (Run 8) consists mainly of walking up and down circular shaped stairs, with small horizontal parts between the segments.
The last type is for Run 3, in which we walked in a straight line, took a $90^{\circ}$ counter-clockwise turn (around the corner) and continued walking.
A more detailed description of the performed activities follows.

\subsection{Outdoor straight lines}\label{subsec:outdoor_straight}
The first series of outdoor performed activities consist of standing still, walking, and running segments in a straight line.
Halfway the recording is a $180^{\circ}$ turn.
The plots of \Cref{fig:plots_subject_1} shows the recordings of Subject $1$.
The recorded metrics originate from the accelerometer, rotational and magnetometer sensors.
The solid black lines indicate manually annotated change points.
A still from the video recording, showing Subject $2$ performing a (sprinting) run segment, is in \Cref{fig:stills_subject_2_sprinting}.

% ===== OUTDOOR FREE ACTIVITIES ========
\subsection{Outdoor free}\label{subsec:outdoor_free}
The second series of outdoor recordings consist of more free-form activities.
The performed activities consist, as with the first set, of standing, walking, and running.
Furthermore, the segments are performed in a circular manner.
\eg the running activities are performed around a fountain with an estimated diameter of 10 meters.
The plots of the recordings of Subject 2, for the accelerometer, rotation, and magnetometer are shown in \Cref{fig:plots_subject_2}.
For Subject~$2$ the still of the video recordings are in the upper row of \Cref{fig:stills_subject_1_and_2}, for Subject~$1$ in the lower row.

@@

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
    \caption{Magnetic Field}
    \label{fig:recording_subject_1_run_1_magnetic}
  \end{subfigure} \\
  \caption[Plots run 1]{Annotated plots of a full recording performed by Subject~$1$. The vertical lines are manually determined change points. The label above each segment indicates the current performed activity.}\label{fig:plots_subject_1}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-5-run-fountain-jos/data_plot_acc_annotated.eps}
    \caption{Accelerometer}
    \label{fig:recording_subject_2_run_5_accelerometer}
  \end{subfigure}

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-5-run-fountain-jos/data_plot_rot_annotated.eps}
    \caption{Rotation}
    \label{fig:recording_subject_2_run_5_rotation}
  \end{subfigure} \\

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-5-run-fountain-jos/data_plot_mag_annotated.eps}
    \caption{Magnetic Field}
    \label{fig:recording_subject_2_run_5_magnetic}
  \end{subfigure} \\
  \caption[Plots run 5]{Annotated plots of a full recording performed by Subject~$2$. The vertical lines are manually determined change points. The label above each segment indicates the current performed activity.}\label{fig:plots_subject_2}
\end{figure}

@@

\subsection{Indoor stairs}\label{subsec:indoor_stairs}
The final series of activities recorded consist of walking up and down the stairs, indoor.
The stairs are shaped in an semi-circular form, with a small horizontal segment on each floor.
The still of \Cref{fig:stills_subject_3_downstairs} illustrates the circular shape of the stairs.
In \Cref{fig:stills_subject_3_upstairs} the small flat segment is visible.
Between the stairs the subject walked in a hallway with a $180^{\circ}$ counter-clockwise turn, as shown in \Cref{fig:stills_subject_3_walking}.
The recorded sensor data of the performed activities are visible in the plots of \Cref{fig:data_gathering_run_3_rot,fig:data_gathering_run_3_mag,fig:data_gathering_run_3_acc}.

### 2014-01-09 Chapters/Chapter6/data_sets.tex
Finalizing.... still....and again...

Because of the above described shortcomings of commonly used data sets, we have decided to record activities by ourselves.
The following characterization requirements were set for our data sets:
\begin{enumerate}
  \item The activities need to be performed and recorded in a continuous manner,
  \item The environment should be natural and uncontrolled, both in- and outdoor,
  \item There data should be clearly annotated, as objective as possible,
  \item The required hardware (and software) should be widely available.
\end{enumerate}

With these requirements in mind, we have created the following setup.
All activities were recorded by a smartphone in the right front pants pocket of the subject.
The phones that were used are the \textsc{HTC Sensation XE} and \textsc{HTC Desire}, running the \textsc{Anroid} smartphone operating system.
During the activities the intertial sensor data is recorded using a free application, \textsc{Sensor Logger}~\cite{sensorlogger}.
This application records the sensor data to \textsc{CSV} files, which are then transformed to \textsc{MATLAB} compatible files.
The constructed algorithm processes the data in an online manner (using only current and historic data).
During the activities, the subject is recorded with a video camera to enable manual labeling and determination of the change points.

Using the video recordings, the data sets are manually annotated, as shown in the plots of \Cref{fig:plots_subject_1,fig:plots_subject_3}.
The graph displays from a single recording the rotational-axis values (see \Cref{tab:recorded_metrics} for explanation of the metrics), with manually annotated activities above the data.
The manually determined change points are used to draw quality conclusion over the algorithm's performance, by comparing it to the discovered change points.
All used data recordings, including the video material and manual labeling, are made available \cite{vlasveld2013continuous}.
\TODO{Create web page with data sets}
The following section discusses the performed activities during the recordings.

>>>>

Because of the above described shortcomings of commonly used data sets, we have decided to record activities by ourselves.
The following characterizing requirements were set for our data sets:
\begin{enumerate}
  \item The activities need to be performed and recorded in a continuous manner,
  \item The environment should be natural and uncontrolled, both in- and outdoor,
  \item There data should be clearly annotated, as objective as possible,
  \item The required hardware (and software) should be widely available.
\end{enumerate}

With these requirements in mind, we have created the following setup.
All activities were recorded by a smartphone worn on body in the right front pants pocket of the subject.
The used phones are the \textsc{HTC Sensation XE} and \textsc{HTC Desire}, running the \textsc{Android} smartphone operating system.
During the activities the intertial sensor data is recorded using a free application, \textsc{Sensor Logger}~\cite{sensorlogger}.
This application records the sensor data to \textsc{CSV} files, which are then transformed to \textsc{MATLAB} compatible files.
The constructed algorithm processes the data in an online manner (using only current and historic data).
The \textsc{MATLAB} implementation uses the \gls{svdd} library \textsc{dd\_tools} by Tax \cite{Ddtools2013}.
During the activities, the subject is recorded with a video camera to enable manual labeling and determination of the change points.
As illustrated in the top row of \Cref{fig:stills_subject_1_and_2}, the manual labeling is an ambiguous task.
In \Cref{fig:stills_subject_2_change_point} a transition between walking and running is shown.
It is impossible to determine the exact location of the change point and thus objective quality measures (such as the delay) are of less importance.

Using the video recordings, the data sets are manually annotated, as shown in the plots of \Cref{fig:plots_subject_1,fig:plots_subject_2,fig:plots_subject_3}.
The graphs display each from a single recording the inertial sensor values (see \Cref{tab:recorded_metrics} for explanation of the metrics), with manually annotated activities above the data.
The manually determined change points are used to draw quality conclusion over the algorithm's performance, by comparing it to the discovered change points.
All of the used data sets, including the video material and manual labeling, are made publicly available \cite{vlasveld2013continuous} for further research.
\TODO{Publish web page with data sets}
The following section discusses the performed activities during the recordings.

### 2014-01-09 Chapters/Chapter6/results.tex
Fill table real-world results
Finalizing.... still....and again...

% !TEX root = ../../main.tex
\section{Results}\label{sec:real_world_results}

\TODO{Add notion of \textbf{empirical} results.}

In the first paragraph we will explain that we use the same quality measures as used in \Cref{sec:artificial_data_quality_metrics} for objective tabular results.
We further argue that more important is the subjective, visual, inspection of the discovered change points regarding the sensor data.
To give both results, we will first give a table and box plot, like in \Cref{sec:artificial_data_results}.
After that, we will show characterizing parts of the plots with annotated and discovered change points.

\subsection{Objective measure}

\TODO{Table of search run (in the columns) and for each run the ratio of False Alarm Rate, Average benefit (closest CP) and STD benefit. Like chapter 5.}

\begin{table}
  \centering
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|c|c|c|c|}
    \cline{2-9}
    \multicolumn{1}{l|}{} & Run 1 & Run 2 & Run 3 & Run 4 & Run 5 & Run 6 & Run 7 & Run 8 \\
    \hline
    Window length & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    Sigma of \gls{rbf} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    High threshold & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    Low threshold & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    Closeness & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    \hline
    $\operatorname*{far}(Y)$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    $\operatorname*{Average\_delay}$ & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
    STD Delay & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    \hline
  \end{tabulary}
  \caption[Results real world runs]{Parameter settings and results of the real-world data sets.}
  \label{tab:results_real_world}
\end{table}

Here something to refer to \Cref{fig:boxplot_real_world_runs}, about what it shows.

@@

We will state observations and remarks from the results which present and applicable to all the runs.
After that, we will discuss special observations for each run individually.

\TODO{Uitleggen over sensitivity: we willen die zo laag mogelijk vanwege stabiliteit.}

About the overall performance and results, we have the following observations:
\begin{itemize}
  \item \textbf{Merging:} in our method we use a \emph{closeness} time period $t_c$ (usually up to $0.5$ - $1.0$ seconds) to merge discovered change points that have a very small distance between them.
  Multiple merging-strategies can be applied, and in our method we use the naive implementation by simply ignoring all the discovered change points that occur less than $t_c$ seconds after the previous change point.
  This works well when there is a block of noisy data with a high amount of (falsely) discovered change points.
  On the flip side, this method will ignore real new change points which occur during the noisy period.
  This problem on itself can be formulated as a change detection problem.
  \item \textbf{Masking:} Since the parameters for the detection method are set globally, it is difficult to discover all the change points (and only the change points) without a high \gls{far}.
  If a change point is proceeded by a noisy block, then the real change point will be merged with the previous change points.
  In an other case, where a change point is very clear represented in the data but the next, close by, other change point is more subtle, the latter change point is \emph{masked} by the former.
  This masking effect is also discussed in \cite{inclan1994use}, where an iterated approach is applied.
  \item \textbf{False heterogeneity:} For our video-data synchronization, we started and ended each recording with a few seconds in which the recording smartphone was kept still in the air.
  During this period, the data variance, and thus the constructed hypersphere, becomes very small.
  As a results, even small movements are considered to be changes and in the case of the mid-air still smartphone a lot of false change points are detected.
  Due to the merging effect described above, the final real change point (often shaking the smartphone) is not discovered.
  \item \textbf{Incorrect weighting:} In our analyses we have used the data from the accelerometer, magnetic field, and rotation sensors.
  In the segments which embodied movement in a circular manner (such as walking around a corner on the street, as in run 3 \TODO{add ref to image}), the turn was not discovered.
  Alternatively, when we only used the magnetic field and rotation sensors, the turn was correctly discovered.
  Other transitions, such as from walking to running, are harder to discover without the (linear) accelerometer sensor data.
\end{itemize}

@@

  \item \textbf{Subject 2, straight}

@@

  \item \textbf{Subject 1, straight}

@@

  \item \textbf{Subject 2, corner}

@@

  \item \textbf{Subject 2, fountain}

@@

  \item \textbf{Subject 1, fountain}

@@

  \item \textbf{Subject 2, fountain 2}

@@

  \setcounter{enumi}{7}

@@

\TODO{Add suggestion for adaptive parameter tuning, locally determined}

Here comes a list of observations and conclusions on the performance:
\begin{itemize}
  \item \textbf{Perhaps something in bold:} here we list a funny observation.
  \eg that when walking the circulair stairs it is harder to find the rotation on the flat surface.
  \item Or just something else.
\end{itemize}

\subsection{Subjective measures}
In this subsection we will provide a few plots with characterizing parts of the sensor data, annotated change points, and discovered change points.
We use it to illustrate some aspects of the method, on which it performs well and where not.
We do not provide all plots, because that would take up to much time.
We do try to give a subjective conclusion about the performance, backed by the provided examples.

\subsection{Notes: remarks}
Mergen van change points:\\

Aanpak 1: Na ieder gevonden change point een bepaalde periode $s$ alle anderen negeren. Probleem: je hebt dan bijna altijd na $s$ sowieso een `gevonden' change point.\\
Aanpak 2: Alle change points die binnen $s$ van elkaar zitten mergen. Probleem: naar voren of naar achteren doen? Als je een heel lang blok hebt met CPs dicht bij elkaar, met mogelijk `echte' CPs, dan worden die ook genegeerd. Mogelijke oplossing: gebruik van `zekerheid' over de gevonden CPs om te mergen.

Het ghosting treedt vooral op aan het begin van iedere run, met het `kaliberen': het begin van de echte activiteit zit er te dicht op en wordt niet goed herkend.

Run 1 - Roemer\\

\begin{itemize}
  \item Doordat de thresholds niet adaptief zijn, wordt de gevoeligheid voor de hele methode globaal gezet.
  Dit zorgt dat ruwe overgangen gevonden worden, maar subtielere worden overgeslagen.
  Bijvoorbeeld: op 14s zit een overgang van rennen naar lopen, maar die is niet zo groot. Deze wordt niet gevonden, tenzij de gevoeligheid veel hoger gaat, maar dan krijg je weer teveel false positives. De overgang vlak erna, op 17s, gaat weer van lopen naar rennen en die wordt wel gevonden.
  \item Op 33s van rennen naar lopen wordt juist weer wel goed gevonden.
  \item Doordat in de data soms wel veranderingen zitten (die niet direct duidelijk zijn uit de video beelden) en change points dichtbij gemerged worden, kan er soms een groot verschil ontstaan. Bv op 8s en 9s. De changes op 7s en 10s worden gemist.
  \item De overgang van rennen naar sprint(?) op 31s wordt gemist.
\end{itemize}

Run 2 - Jos \\
\begin{itemize}
  \item Op 37s is een annotate van rennen naar lopen. De methode detecteert het bijna een seconde eerder. Als je naar de ruwe data kijkt zie je daar ook een verandering, dus nog voordat je het uit de video-beelden zou opmerken --> heel subjectief dus.
  \item Zelfde `ghosting' probleem als hierboven: bij overgang van Still naar Pocket wordt niets gevonden, doordat in de periode ervoor veel changes zijn. De data in `Still' is heel homogeen, dus kleine veranderingen worden als changes gezien, en die zijn er alsnog veel. --> \textbf{Hoe heterogener de data, hoe robuster}.
\end{itemize}

Run 3 - Roemer, around the corner \\
\begin{itemize}
  \item Met acc, mag, rot data is 90 graden CCW niet goed te vinden. Met mag,rot data wel --> te veel data is ook niet goed.
  \item Het enige punt, de draai, wordt met mag,rot goed gevonden. (geen plot of data, want verder niet interessant). Ook Walk-in-hand, pocket en Out-pocket worden erg nauwkeurig gevonden!
\end{itemize}

Run 4 - Roemer, fountain \\
\begin{itemize}
  \item Na 24s: van Rennen naar Lopen, worden meerdere change points gevonden. In de data zie je ook dat iedere stap een rustigere stap is, dus de gevoeligheid pakt dat op.
  \item De draaien in het Rennen rond 12s en 16s worden wel gevonden (bij hoge gevoeligheid, met delay), maar die rond 21s niet. (acc, mag, rot). Met alleen Rot ook niet.
  \item Correct number of change points found, but still 11 total difference. Would be better if benchmarking periods (still, shake) would not be present. (overall geldt dat ook).
  \item
\end{itemize}

Run 5 - Jos, fountain \\
\begin{itemize}
  \item Bij Acc,Mag,Rot worden de Turn CW punten niet goed gevonden. Bij alleen Rot wel (niet allemaal, maar wel beter).
  \item Om bij Acc,Mag,Rot de Turn te vinden is hoge gevoeligheid nodig, maar dat geeft hoge FAR.
  \item
\end{itemize}

Run 6 - Roemer, fountain \\
\begin{itemize}
  \item Om de overgang van rennen naar lopen op 18s te vinden is relatief hoge Low-threshold nodig (dus: hoge gevoeligheid).
  \item Bij hoge Low-Threshold wordt draai op 24s ook gevonden. Anders niet.
  \item Stilstaan op 38s geeft hele veel ruis in `thresholding' property. --> overgang naar lopen 2 sec later wordt niet goed gevonden. Komt doordat hypersphere heel klein wordt, en dus veel outliers?
  \item
\end{itemize}

Run 7 - Jos, fountain \\
Camera was leeg, dus mislukte run

Run 8 - Marc, indoor \\
\begin{itemize}
  \item Op 24s, van Walk naar Downstairs: door het ghosting effect is het moeilijk te pakken. Relatief hoge merging-tijd nodig, maar dat verwijderd deze, omdat het begin van lopen dicht zit op het begin van downstairs.
  \item Op 37s zit CCW Turn: is te herkennen (met acc, mag, rot) maar hoge gevoeligheid nodig.
  \item In tweede downstairs block (24s) en upstairs blocken (42s, 54s) worden halverwege ook changes gevonden (met acc, mag, rot). Ook met alleen Acc: zit ook echt verschil in de data
  \item Met alleen Mag data heel veel changes: cirkel-vorm van trap zorgt voor constante verandering.
  \item Overall: hoge FAR, door cirkelvorm trap (?)
  \item Verschil tussen down/upstairs en lopen is niet zo groot. Typisch: 33/34s: herkenning van overgang duurt even een stap.
  \item Vooral op einde, vanaf 66s (lopen naar stoel), heel veel False Positives. Veel verschillende activiteiten kort op elkaar.
\end{itemize}

>>>>

% !TEX root = ../../main.tex
\section{Results}\label{sec:real_world_results}
In this section we will provide the results of our methods applied to the real-world data sets and discuss the quality of the solution.
As stated above, we will use the objective quality metrics as used in \Cref{sec:artificial_data_quality_metrics}.
That will be in the form of a tabular overview of the (manually set) best meta-parameters and results, expressed in \gls{far} and $\operatorname*{Average\_delay}$ (following \Cref{sec:artificial_data_results}).
Furthermore, we will discuss the results from an empirical point of view, since the problem of finding change points in human activities is ambiguous.
By stating our observations and remarks and providing fragments of visual results, we will discuss the characterizing strengths and weaknesses of our method.

\subsection{Objective metrics}
The employed two-stage algorithm requires the setting of user defined parameters.
In \Cref{tab:results_real_world} for each run the results are listed, together with the used parameters.
We have used a window length of 50 frames, which represents around $1.16$ seconds of data (the frame-rate of the recordings is not fixed, and we apply a slight filtering).
The other parameter values are the result of an educated guess and manual optimization.
In general, a high value for the upper threshold and low value for the lower threshold indicates a robust method, since it indicates that change points are significantly different from homogeneous segments.
The closeness time frame should be low, since that indicates there are few false positives.

\begin{table}
  \centering
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|c|c|c|}
    \cline{2-8}
    \multicolumn{1}{l|}{} & Run 1 & Run 2 & Run 3 & Run 4 & Run 5 & Run 6 & Run 7 \\
    \hline
    Window length & 50 & 50 & 50 & 50 & 50 & 50 & 50 \\
    \hline
    Sigma of \gls{rbf} & 13 & 13 & 13 & 13 & 13 & 13 & 4 \\
    \hline
    High threshold & 1.2 & 1.5 & 1.3 & 1.1 & 1.3 & 1.2 & 1.7 \\
    \hline
    Low threshold & 0.8 & 0.8 & 0.6 & 0.7 & 0.7 & 0.8 & 0.6 \\
    \hline
    Closeness (s) & 0.7 & 0.85 & 1 & 0.6 & 0.7 & 1 & 0.8 \\
    \hline
    \hline
    $\operatorname*{far}(Y)$ & 0.1 & 0.05 & 0 & 0 & 0.2 & 0 & 0.48 \\
    \hline
    $\operatorname*{Average\_delay}$ & 0.52 & 0.83 & 0.47 & 0.92 & 1.26 & 1.05 & 0.92 \\
    \hline
    STD Delay & 0.29 & 0.55 & 0.52 & 0.75 & 1.67 & 0.78 & 0.92 \\
    \hline
  \end{tabulary}
  \caption[Results real world runs]{Parameter settings and results of the real-world data sets.}
  \label{tab:results_real_world}
\end{table}

To give a better impression on the quality of the $\operatorname*{Average\_delay}$, \Cref{fig:boxplot_real_world_runs} shows a box plot for each run.
It shows the spread of the $\operatorname*{Average\_delay}$ in seconds over all the change points.
A lower and more compact box plot is better.

@@

\subsection{Subjective observations and remarks}
Since the manual annotation of change points is ambiguous, the objective quality metrics can give a distorted view of the performance.
To overcome this, we will state observations and remarks found after close (visual) inspection of the annotated and discovered change points.
We will start with general observations applicable to all the runs and will continue with individual remarks for each run.
Where possible, a graphical illustration will support our observations.

Considering the overall performance and results, we have the following observations:
\begin{itemize}
  \item \textbf{Merging:} in our method we use a \emph{closeness} time period $t_c$ (usually up to $0.5$ - $1.0$ seconds) to merge discovered change points that have a very small distance between them.
  Multiple merging-strategies can be applied, and in our method we use the naive implementation by simply ignoring all the discovered change points that occur less than $t_c$ seconds after the previous change point.
  This works well when there is a block of noisy data with a high amount of (falsely) discovered change points.
  On the flip side, this method will ignore real new change points which occur during the noisy period.
  This problem on itself can be formulated as a change detection problem.
  \item \textbf{Masking:} Since the parameters for the detection method are set globally, it is difficult to discover all the change points (and only the change points) without a high \gls{far}.
  If a change point is proceeded by a noisy block, then the real change point will be merged with the previous change points.
  In an other case, where a change point is very clear represented in the data but the next, close by, other change point is more subtle, the latter change point is \emph{masked} by the former.
  This masking effect is also discussed in \cite{inclan1994use}, where an iterated approach is applied.
  \item \textbf{False heterogeneity:} For our video-data synchronization, we started and ended each recording with a few seconds in which the recording smartphone was kept still in the air.
  During this period, the data variance, and thus the constructed hypersphere, becomes very small.
  As a results, even small movements are considered to be changes and in the case of the mid-air still smartphone a lot of false change points are detected.
  Due to the merging effect described above, the final real change point (often shaking the smartphone) is not discovered.
  \item \textbf{Incorrect weighting:} In our analyses we have used the data from the accelerometer, magnetic field, and rotation sensors.
  In the segments which embodied movement in a circular manner (such as walking and running around a fountain), the turn was not (or at a different time point) discovered.
  Alternatively, when we only used the magnetic field and rotation sensors, the turn was correctly discovered.
  Other transitions, such as from walking to running, are harder to discover without the (linear) accelerometer sensor data.
\end{itemize}

@@

  \item \textbf{Subject 2, straight walk and run}

@@

  \item \textbf{Subject 1, straight walk and run}

@@

  \item \textbf{Subject 2, walk around corner}

@@

  \item \textbf{Subject 2, walk and run around fountain}

@@

  \item \textbf{Subject 1, walk and run around fountain}

@@

  \item \textbf{Subject 2, walk and run fountain 2}

@@

@@

\TODO{Samenvatten observations en remarks, brugje naar possible improvements maken}

\section{Possible improvements}\label{sec:possible_improvements}
From the above section we can extract a few possible improvements for the algorithm.
Most of the observations and remarks are due to a different required sensitivity for local segments of the run.
Currently, our method employs a global setting for the thresholds.
A possible improvement would be to use locally optimized parameters, although that would require an reflective data processing approach or more a priori about the data.
With our approach, the lack of a priori knowledge about the data distribution is one of the design decisions.

Furthermore, we discovered that sometimes, especially with movements incorporating circular motions, the addition of (linear) accelerometer data makes the discovery of change points harder.
In such cases, each of the inertial sensor data streams should be relatively weighted (\eg using the covariance) in order to signal an overall change when it only occurs in one of the streams.
